TBD

### 2021-03-16 outputs/paper/paper.Rmd

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "With the growing ubiquity of deepfake technology, here comes one more channel for the spread of misinformation. We reproduce Soubhik Barari (2021) paper and identify several additional demographic traits contributing to the persuasion power of deepfake on political defamation through its material effect on feeling manipulation in a RCT field experiment on the 2020 Presidential election. We find little evidence that deepfake videos have a unique ability to shift viewers’ perceptions on politicians. Apart from partisanship, education, and other socioeconomic factors identified by the original paper, we discover that income and internet usage would also significantly impact the candidate’s affective appeal to the news feed viewer. "
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
editor_options: 
  chunk_output_type: inline

header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}
---

@@

library(tinytex)
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(hrbrthemes)
library(kableExtra)
library(broom)

@@

```{r loaddata, echo=FALSE, warning=FALSE, message=FALSE}
library(here) # locate the file path

data<- load(here::here("inputs/data/deepfake.RData"))

EDA<- dat%>%
        select(treat, response_wave_ID, exp_1_prompt, meta_OS, age_65, educ, PID, crt, gender, age, polknow, internet_usage, ambivalent_sexism, post_favor_Warren,believed_true)

@@

```{r ttest1, echo=FALSE, fig.width=10, fig.height=3}
t1<-t.test(na.omit(dat$believed_true[dat$treat_fake_video == 1]), 
       na.omit(dat$believed_true[dat$treat_fake_audio == 1]))

m1<-tidy(t1, digits=1)
m1 %>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_deception_video=estimate1,
    AVG_deception_audio=estimate2
  )%>%
  kableExtra::kbl(caption="T test: Deception level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

```{r attest1, echo=FALSE, fig.width=10, fig.height=3}
#video vs control
t1_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_control == 1]))

@@

```{r attest2, echo=FALSE, fig.width=10, fig.height=3}
#video vs text
t2_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_text == 1]))

@@

Table \@ref(tab:attest3) shows the test result of how deepfake videos and audios impact audiences' feelings. The difference in affect level between video(Mean = 41.28) and audio (Mean=43.93) was not significant given the p-value is greater than 0.05.
```{r attest3, echo=FALSE, fig.width=10, fig.height=3}
#video vs audio
t3_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_audio == 1]))

@@

Table \@ref(tab:attest4) shows the test result of how deepfake videos and skit impact audiences feeling. The difference in affect level between video(Mean = 41.28) and skit (Mean=43) was not significant given the p-value is greater than 0.05.
```{r attest4, echo=FALSE, fig.width=10, fig.height=3}
#video vs skit
t4_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_skit == 1]))

@@

```{r fs, echo=FALSE, fig.width=10, fig.height=10,results=FALSE,message=FALSE,include=FALSE }

## Feature selection 
# library(randomForest)
# library(plyr)

# deal with missing value
FS<- dat%>%
 select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Sanders,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake,exp_2,exp_2_prompt_accuracy,exp_2_after_debrief,exp_2_prompt,Zip,believed_true))%>% na.omit()
## feature selection 
#set.seed(123)
#FS_tree<-randomForest(post_favor_Warren~., data=FS, ntree=500, importance=TRUE,proximity=TRUE) ## variable importance

#FS_tree<-as.data.frame(FS_tree$importanceSD) # transform to dataframe

#FS_tree<- FS_tree[order(-FS_tree[,]),,drop=FALSE] # sort importance by descending order

#FS_tree<- cbind(Variable_name = rownames(FS_tree), FS_tree)
#rownames(FS_tree) <- 1:nrow(FS_tree)
#FS_tree<- as.data.frame(FS_tree)

@@

#FS_tree%>%
  #mutate(name = fct_reorder(FS_tree$Variable_name,FS_tree$`FS_tree$importanceSD`))%>%
  #ggplot(aes(x=FS_tree$Variable_name, y=FS_tree$`FS_tree$importanceSD`)) +
  #geom_segment( aes(x=FS_tree$Variable_name,xend=FS_tree$Variable_name, y=0, yend=FS_tree$`FS_tree$importanceSD`), color="grey") +
  #geom_point( color="orange", size=4) +
  #theme_light() +
  #coord_flip()+
  #theme(
    #panel.grid.major.x = element_blank(),
   # panel.border = element_blank(),
   # axis.ticks.x = element_blank()
 # ) +
 # xlab("") +
 # ylab("Importance value")+
#  ggtitle("Variable importance plot")

## remove low importance feature 
#FS<- FS%>%select(-c(script_loans,quality,Hispanic))
```

## Multiple Linear Regression Results

### Model Results
Multiple linear regression was applied to use the top 20 important explanatory variables generated from the random forest model to predict the affect level.

@@

```{r, echo=FALSE, warning=FALSE, fig.width=10, fig.height=4,message=FALSE}

## transfer data into dummy
#library(fastDummies)

#Dummy_data<- fastDummies::dummy_cols(FS, remove_first_dummy = TRUE, #remove_selected_columns = TRUE)%>%
#  select(-c(4))#  change categorical var to factors

##create model

@@

@@

###

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"

abstract: "With the growing ubiquity of deepfake technology, here comes one more channel for the spread of misinformation. We reproduce Soubhik Barari (2021) paper and identify several additional demographic traits contributing to the persuasion power of deepfake on political defamation through its material effect on feeling manipulation in a RCT field experiment on the 2020 Presidential election. We find little evidence that deepfake videos have a unique ability to shift viewers’ perceptions on politicians. Apart from partisanship, education, and other socioeconomic factors identified by the original paper, we discover that income and internet usage would also significantly impact the candidate’s affective appeal to the news feed viewer. "

output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
editor_options: 
  chunk_output_type: inline
header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}
---

@@

library(tinytex)
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(hrbrthemes)
library(kableExtra)
library(broom)
library(randomForest)
library(plyr)
```

@@

```{r loaddata, echo=FALSE, warning=FALSE, message=FALSE}
library(here) # locate the file path
data<- load(here::here("inputs/data/deepfake.RData"))
EDA<- dat%>%
        select(treat, response_wave_ID, exp_1_prompt, meta_OS, age_65, educ, PID, crt, gender, age, polknow, internet_usage, ambivalent_sexism, post_favor_Warren,believed_true)

@@

```{r ttest1, echo=FALSE, fig.width=10, fig.height=3}
t1<-t.test(na.omit(dat$believed_true[dat$treat_fake_video == 1]), 
       na.omit(dat$believed_true[dat$treat_fake_audio == 1]))
m1<-tidy(t1, digits=1)
m1 %>%
  select(-c(estimate,statistic,parameter))%>%
 # rename(
   # AVG_deception_video=estimate1,
   # AVG_deception_audio=estimate2
 # )%>%
  kableExtra::kbl(caption="T test: Deception level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

@@

```{r attest1, echo=FALSE, fig.width=10, fig.height=3}

#video vs control
t1_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_control == 1]))

@@

### T test2

```{r attest2, echo=FALSE, fig.width=10, fig.height=3}

#video vs text
t2_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_text == 1]))

@@

### T test3

Table \@ref(tab:attest3) shows the test result of how deepfake videos and audios impact audiences' feelings. The difference in affect level between video(Mean = 41.28) and audio (Mean=43.93) was not significant given the p-value is greater than 0.05.

```{r attest3, echo=FALSE, fig.width=10, fig.height=3}

#video vs audio
t3_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_audio == 1]))

@@

### T test 4

Table \@ref(tab:attest4) shows the test result of how deepfake videos and skit impact audiences feeling. The difference in affect level between video(Mean = 41.28) and skit (Mean=43) was not significant given the p-value is greater than 0.05.

```{r attest4, echo=FALSE, fig.width=10, fig.height=3}

#video vs skit
t4_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_skit == 1]))

@@

## Feature selection

```{r fs, echo=FALSE, warning=FALSE,fig.width=10, fig.height=10 }
# deal with missing value
FS<- dat%>%
 select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Sanders,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake,exp_2,exp_2_prompt_accuracy,exp_2_after_debrief,exp_2_prompt,Zip,believed_true))%>% na.omit()

## feature selection

set.seed(123)
FS_tree<-randomForest(post_favor_Warren~., data=FS, ntree=500, importance=TRUE,proximity=TRUE) ## variable importance

FS_tree<-as.data.frame(FS_tree$importanceSD) # transform to dataframe

FS_tree<- FS_tree[order(-FS_tree[,]),,drop=FALSE] # sort importance by descending order

FS_tree<- cbind(Variable_name = rownames(FS_tree), FS_tree)
rownames(FS_tree) <- 1:nrow(FS_tree)
FS_tree<- as.data.frame(FS_tree)

@@

FS_tree%>%
  mutate(name = fct_reorder(FS_tree$Variable_name,FS_tree$`FS_tree$importanceSD`))%>%
  ggplot(aes(x=FS_tree$Variable_name, y=FS_tree$`FS_tree$importanceSD`)) +
  geom_segment( aes(x=FS_tree$Variable_name,xend=FS_tree$Variable_name, y=0, yend=FS_tree$`FS_tree$importanceSD`), color="grey") +
  geom_point( color="orange", size=4) +
  theme_light() +
  coord_flip()+
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  xlab("") +
  ylab("Importance value")+
  ggtitle("Variable importance plot")

## remove low importance feature 
FS<- FS%>%select(-c(script_loans,quality,Hispanic))
```

### Model Results

Multiple linear regression was applied to use the top 20 important explanatory variables generated from the random forest model to predict the affect level.

@@

```{r model, echo=FALSE, warning=FALSE, fig.width=10, fig.height=4,message=FALSE}

## transfer data into dummy
#  select(-c(4))#  change categorical var to factors 
##create model

@@

```{r diagnostic, echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
#install.packages("see")
library(performance) ## creates a ggplot2-based graphics 
performance::check_model(model)
```

```{r model_improved, echo=FALSE, warning=FALSE, fig.width=10, fig.height=2}
#model2 <- lm(sqrt(post_favor_Warren)~., data = FS)
#autoplot(model2,3)
```

@@

```{r modelsummary, echo=FALSE, warning=FALSE, fig.width=8, fig.height=10}
#install.packages("modelsummary")
library(modelsummary)

ms<-
modelsummary(
model,
output = "default",
fmt = 3,
estimate = "estimate",
statistic = "std.error",
vcov = NULL,
conf_level = 0.95, #confidence level to use for confidence intervals
stars = TRUE,
align = NULL,
notes = NULL,
title = "Regression results")

ms%>%
  kableExtra::kable_styling(bootstrap_options = "basic",
                            latex_options = "HOLD_position",
                            table.envir = "table",
                            font_size =5
                           )
